\input ../header/example_tex01.tex

% \FFrf \baselineskip = 14pt
  \FFrg \baselineskip = 15pt

{
Yanuo Deng (James)
}

{ 
% \FFrb
1565 Cress Way, Olivehurst,CA,95961
*
(408)444-5520
*
deng.ya.nuo@gmail.com
}

{ \smallbreak } 

{\par\noindent\hrule} 

{ \bigbreak } 


Aruba Networks, Roseville, CA, 95757

{ 
%Dear Shawn Taylor,
Dear Hiring Manager,
}

{ \bigbreak } 
I am applying for the position of `` Embedded Software Engineer '' in your esteemed Aruba Network company.

{ \bigbreak } 
I believe I am the right candidate for the position .
I have a MSc in Microelectronics \& Solid State Electronics.
My 15+ years of experience, among others, 
includes a dual-MIPS SOC chip designing ,
Linux kernel triming  /  driver porting , 
FreeRTOS driver porting  /  task coding,
and bootloader coding.

{ \bigbreak } 
I am committed to achieving results and working long hours 
to achieve them is not a problem as evidenced by 
delivering at the rate of one IP core per month,
with the SOC passing at first tapeout
with a US patent awarded.

{ \bigbreak } 
During developing  /  porting device drivers for Linux / FreeRTOS,
I know what happened inside the CPU when writing to the registers,
which give me some advantage at bootloader  /  driver developing .

{ \bigbreak } 
I have WiFi driver developing / debug experience. 
I wrote UDP sender / receiver by FPGA leading me know every bit in the network transport layer.
I use git  /  gnumake  /  bash  /  perl  /  sed  /  grep  /  vim as my deverloping tools.
During prototype developing, I use mathematica / Golang / perl, 
while Golang / C / verilog / FPGA will be used to verify the system.

{ \bigbreak } 
I hope my background meets your needs and I look
forward to elaborating on how my specific skills and abilities will benefit your Aruba Network company.

{ \bigbreak } 
I can be contacted at deng.ya.nuo@gmail.com
or (408)444-5520 to arrange for a convenient time to meet.

{ \bigbreak } 




\vskip 60pt

{ \bigbreak } 
Sincerely,

Yanuo Deng (James)

\bye
