\special{papersize=8.5in,11.5in}

% % 0.4 padding 
% \hsize 7.7 in     % 8.5  - 0.4 * 2
% \vsize 10.7 in    % 11.5 - 0.4 * 2
% \voffset -0.6 in  % 1 - 0.4
% \hoffset -0.6 in  % 1 - 0.4

% % 0.2 padding 
% \hsize 6.9 in     % 8.5  - 0.8 * 2
% \vsize 9.9 in     % 11.5 - 0.8 * 2
% \voffset -0.2 in  % 1 - 0.8
% \hoffset -0.2 in  % 1 - 0.8

% 0 padding 
\hsize 6.5 in     % 8.5  - 1 * 2
\vsize 9.5 in     % 11.5 - 1 * 2
\voffset 0 in  % 1 - 0
\hoffset 0 in  % 1 - 0

\nopagenumbers

\parindent = 0 pt
\emergencystretch = 800 em
%\tolerance=10000
\baselineskip = 18pt
%\baselineskip = 16pt
%\baselineskip = 12pt


\font\FFba=      cmb10            at 8.5pt
\font\FFbb=      cmb10            at 10pt
\font\FFbc=      cmb10            at 12pt
\font\FFbd=      cmb10            at 13pt
\font\FFbe=      cmb10            at 16pt
\font\FFbf=      cmb10            at 18pt
\font\FFbg=      cmb10            at 24pt

\font\FFra=      cmr10            at 8.5pt
\font\FFrb=      cmr10            at 10pt
\font\FFrc=      cmr10            at 12pt
\font\FFrd=      cmr10            at 13pt
\font\FFre=      cmr10            at 16pt
\font\FFrf=      cmr10            at 18pt
\font\FFrg=      cmr10            at 24pt

\font\FFta=      cmti10           at 8.5pt
\font\FFtb=      cmti10           at 10pt
\font\FFtc=      cmti10           at 12pt
\font\FFtd=      cmti10           at 13pt
\font\FFte=      cmti10           at 16pt
\font\FFtf=      cmti10           at 18pt
\font\FFtg=      cmti10           at 24pt


\FFrd

{
Yanuo Deng (James)
}

{ 
% \FFrb
1565 Cress Way, Olivehurst,CA,95961
*
(408)444-5520
*
deng.ya.nuo@gmail.com
}

{ \smallbreak } 
{\par\noindent\hrule} 
{ \medbreak } { 
}

%{ \medbreak } { 
%Shawn Taylor
%}
%
%Associate Director at Microchip Technology, Roseville, CA
%
%\vskip 30pt

%{ \medbreak } 
%\vskip 10pt
{ \bigbreak } 

{ 
%Dear Shawn Taylor,
Dear Hiring Manager
}

{ \bigbreak } 
I am applying for the position of ``ASIC Engineer'' position in your esteemed company.

{ \bigbreak } 
I believe I am the right candidate for the position as I have a MSc in Microelectronics \& Solid State Electronics.
My 15+ years of experience, among others, 
includes designing a dual-MIPS SOC with a Security Engine inside. 
I wrote all the IP cores consisting of AES, DES, 3DES, MD5, SHA1, CRC 
used to speed up the DICE + RIoT security cryptography.
Each IP core was about 3000 to 5000 lines in Verilog HDL, 
activities included designing and testing the RTLs \& Netlist,
and timing check rules for simulation and place \& route.

{ \bigbreak } 
I am committed to achieving results and working long hours 
to achieve them is not a problem as evidenced by 
delivering at the rate of one IP core per month,
with the SOC passing at first tapeout
with a US patent US7356671B1 awarded.

{ \bigbreak } 
I am also experienced as an embedded engineer using Linux + VxWorks, 
analogy simulatinon tool Hspice, 
and prototyping using Xilinx/Altera FPGA boards.

{ \bigbreak } 
I hope my background meets your needs and I look
forward to elaborating on how my specific skills and abilities will benefit your company.

{ \bigbreak } 
I can be contacted at deng.ya.nuo@gmail.com
or text to (408)444-5520 to arrange for a convenient time to meet.

{ \bigbreak } 




\vskip 60pt

{ \bigbreak } 
Sincerely,

Yanuo Deng (James)

\bye
