\input ../header/example_tex01.tex

{
Yanuo Deng (James)
}

{ 
% \FFrb
1565 Cress Way, Olivehurst,CA,95961
*
(408)444-5520
*
deng.ya.nuo@gmail.com
}

{ \smallbreak } 
{\par\noindent\hrule} 
{ \medbreak } { 
}

%{ \medbreak } { 
%Shawn Taylor
%}
%
%Associate Director at Microchip Technology, Roseville, CA
%
%\vskip 30pt

%{ \medbreak } 
%\vskip 10pt
{ \bigbreak } 

eInfochips , Irvine, CA

{ 
%Dear Shawn Taylor,
Dear Hiring Manager
}

{ \bigbreak } 
I am applying for the position of ``Design Engineer'' in your esteemed eInfochips company.

{ \bigbreak } 
I believe I am the right candidate for the position as I have a MSc in Microelectronics \& Solid State Electronics.
My 15+ years of experience, among others, 
includes designing a dual-MIPS SOC with a Security Engine inside. 
I wrote all the IP cores consisting of AES, DES, 3DES, MD5, SHA1, CRC 
used to speed up the DICE + RIoT security cryptography.
Each IP core was about 3000 to 5000 lines in Verilog HDL, 
activities included designing and testing the RTLs \& Netlist,
and timing check rules for simulation and place \& route.

{ \bigbreak } 
I am committed to achieving results and working long hours 
to achieve them is not a problem as evidenced by 
delivering at the rate of one IP core per month,
with the SOC passing at first tapeout
with a US patent US7356671B1 awarded.

{ \bigbreak } 
I am also experienced at using Linux / VxWorks, 
analogy simulatinon tool Hspice, 
and prototyping using Xilinx/Altera FPGA boards.

{ \bigbreak } 
I have experiences at Linux kernel trimming, bootloader coding, embedded Linux systems porting at ARM/MIPS, and FreeRTOS porting at STM32.

{ \bigbreak } 
I hope my background meets your needs and I look
forward to elaborating on how my specific skills and abilities will benefit your eInfochips company.

{ \bigbreak } 
I can be contacted at deng.ya.nuo@gmail.com
or (408)444-5520 to arrange for a convenient time to meet.

{ \bigbreak } 




\vskip 60pt

{ \bigbreak } 
Sincerely,

Yanuo Deng (James)

\bye
