\input ../header/example_tex01.tex

\parskip 1.5 em

% \FFrf \baselineskip = 14pt
\FFrg \baselineskip = 15pt
% \FFrj \baselineskip = 20pt
%   \FFrl \baselineskip = 24pt



%\filltospace{6em}{
\centerline{
\FFrf 
Syed Moheen, Sr Executive - Talent Acquisition, @ L\&T TECHNOLOGY SERVICES LIMITED
} 

\par As discussed, please confirm the salary of \$100 K /Annum + All Benefit.
\par Kindly share me your updated resume.
\par Job title:                                  Firmware Validation Engineer
\par Location:                                 Folsom, CA
\par Duration:                                Full Time (Permanent)
\par Job Description:
\par Ideal candidate should be working as part of pre-silicon and post silicon firmware software integration team for current and next generation Client SOC Products.
\par Strong technical background with hands-on experience in Windows OS Validation and Debug, OS/Product security features is preferred.
\par You will be working on the integration, bring up, and debug of the full FW/SW/HW stack of components on our continuum of pre-silicon and post silicon platforms such as Virtual Platforms, FPGA and Reference design platforms The person should be familiar with SW project life cycle, with ability to work from requirements phase to releases meeting pre-defined quality criteria.
\par Required Skills:
\par Good knowledge in OS internals - Windows
\par Knowledgeable in security basics.
\par Preferred prior knowledge of using test equipment's like O-scope, LA, JTAG etc
\par Strong technical background with hands-on experience in Windows OS Validation and Debug.
\par Developing and utilizing various software tools and/or methodologies with the goal to ensure highly functional firmware
\par Communicating effectively, coordinating and working with firmware developers and SOC integration teams
\par Potentially participating in the debug of failures in silicon and developing new testing strategies to detect these failures on pre-silicon models.
\par windows Platforms.

\bye
