\input ../header/example_tex01.tex

\parskip 1.5 em

% \FFrf \baselineskip = 14pt
% \FFrg \baselineskip = 15pt
\FFrj \baselineskip = 20pt
%   \FFrl \baselineskip = 24pt



%\filltospace{6em}{
\centerline{
Hope Nelson @ Professional Recruiter at Insight Global
} 

\par I came across your profile and think you would be a great fit for an Embedded Engineer opportunity our client has open!
\par This is a direct hire role located in Cincinnati, OH.
\par This person will be responsible for writing firmware for embedded processes and write software code for desktop graphical user interfaces. Design, Analysis and verification testing will be performed as a functional component for new product designs as well as participating in the testing process through test review, witnessing, debugging and certification of the software for its functionality. This individual will be collaborating with hardware engineers to help with the design and development of hardware and may interface with users to define system requirements and/or necessary modifications.
\par Our client is looking for experience in the following areas:
\par • C or C++ programming
\par • Debugging tools like Oscilloscopes, Voltmeters, JTAG, etc.
\par • Knowledge of different interfaces and hardware microcontroller subsystems such as SPI, I2C, CAN, GPIO and RS232/RS485 communication.
\par • Experience working with microcontrollers such as Freescale, PIC and ST.
\par If this is something you would be interested in hearing more about, I'd love to set up a time for us to chat about the details further!
\par Hope Nelson
\par Professional Recruiter at Insight Global

\bye
