\input ../header/example_tex01.tex

\parskip 0.35 em

\FFrf \baselineskip = 14pt
% \FFrg \baselineskip = 15pt
% \FFrj \baselineskip = 20pt
%   \FFrl \baselineskip = 24pt



%\filltospace{6em}{
\centerline{
Hope Nelson @ Professional Recruiter at Insight Global
}
\centerline{
Embedded Engineer @ Teledyne Tekmar @ 4736 Socialville-Foster Rd. Mason, OH 45040
} 

\par It was great speaking with you today and thank you again for your time! Please send two to three managerial references that we can put on file.
\par Please include:
\par Company:
\par Manager Name:
\par Manager Title:
\par Phone number:
\par Email:
\par Lastly, below is a link for our brief (5 minute) job application. Please complete at your earliest convenience.
\par The Job Application Page can be found at: https://www.insightglobal.net/jobApp.php
\par Enter the code: MP14Az5
\par Below I have included the job description we discussed.
\par Company: Teledyne Tekmar
\par Position: Embedded Engineer
\par Duration: Direct Hire
\par Location: 4736 Socialville-Foster Rd. Mason, OH 45040
\par Must haves:
\par 3-5 years of experience in C or C++ and the development including the tools to compile, assemble and debug in an embedded environment.
\par Experience using debugging tools like Oscilloscopes, Voltmeters, JTAG, etc.
\par Knowledge of different interfaces and hardware microcontroller subsystems such as SPI, I2C, CAN, GPIO and RS232/RS485 communication.
\par Experience working with microcontrollers such as Freescale, PIC and ST.
\par Plusses:
\par Experience with board debugging and control of robotic motors, devices and sensors.
\par Comfortable with MS office and cooperative version control systems (SVN)
\par Basic knowledge of ISO and/or AS9100
\par Embedded firmware and RTOS or kernel based systems
\par FPGA
\par Hardware design
\par Free RTAS
\par D2D:
\par An employer in the Mason, OH area is a seeking an Embedded Software/Firmware Engineer for a full time opportunity. This person will be responsible for writing firmware for embedded processes and write software code for desktop graphical user interfaces. Design, Analysis and verification testing will be performed as a functional component for new product designs as well as participating in the testing process through test review, witnessing, debugging and certification of the software for its functionality. This individual will be collaborating with hardware engineers to help with the design and development of hardware and may interface with users to define system requirements and/or necessary modifications.

\bye
