\input ../header/example_tex01.tex

\parskip 0.5 em

\FFrf \baselineskip = 14pt
% \FFrg \baselineskip = 15pt
% \FFrj \baselineskip = 20pt
%   \FFrl \baselineskip = 24pt



%\filltospace{6em}{
\centerline{
Haosen Wang @ Element Biosciences, engineering department
} 

\par I am Haosen from Element Biosciences, engineering department.
\par I see your application for our Embedded system engineer job position.
\par Will you be able to have a 30 mins phone call interview in this week or next week?
\par Let me know the preferred time.

\vfill 

\par About the job
\par Element Biosciences is a multi-disciplinary startup focused on innovating genetic analysis tools for the research and clinical markets. The Company's technology will broaden the end user experience through improved data quality and simplified workflows to benefit discoveries and diagnosis in healthcare.
\par Actively participate in the development of a high-performance instrument control and data processing system. Undertake design and validation tasks on embedded SW/HW, system feature validation and optimization. Expedite system performance evaluation, reliability improvements and new feature implementation.
\par Essential Functions And Responsibilities
\par Work with SW/HW engineers to design and implement embedded system features including HW spec definition, FPGA design, and SW coding
\par Develop and maintain code for ARM microcontrollers
\par Conduct hardware validation and firmware debugging for custom board designs
\par Explore and evaluate optimization opportunities for system operations
\par Support system runtime debugging and issue fix
\par Create documentation with clear organization and consistency
\par Education and Experience
\par Minimum Bachelor’s degree in Electrical Engineering, Computer Science or equivalent field of study (MS degree in same area is a plus) with at least 5 years experience in EE / embedded system development with deep involvement (an equivalent combination of experience and education may be considered)
\par Experience with usual communication protocols: UART, I2C, SPI, CAN etc.
\par Good knowledge about electronic systems, their typical issues, and approaches to debug
\par Proficient in development with C language as well as corresponding debugging tools / methodology; Familiar with FPGA HDL design is a plus
\par Ability to read circuit schematic diagram, examine and evaluate electrical hardware components
\par Motivated team member with good logical thinking and efficient communication skills
\par We are passionate about our mission to develop high performing products to study genomics in an unprecedented flexibility and to understand biology for the improvement of healthcare. We have built a highly efficient product-driven organization where employees can learn, grow and thrive in a challenging but encouraging environment. We are committed to scientific integrity, collegiality, honesty, objectivity, and openness. We offer excellent benefits, which include a 401K plan, competitive health benefits, flexible vacation, and equity incentives.
\par We foster an environment such that all people are afforded the freedom to pursue their passions without regard to race, color, religion, national or ethnic origin, gender (including pregnancy), sexual orientation, gender identity or expression, age, disability, veteran status or any other characteristics protected by law.

\bye
