\input ../header/example_tex01.tex

\parskip 0.5 em

% \FFrf \baselineskip = 14pt
% \FFrg \baselineskip = 15pt
\FFrh \baselineskip = 16pt
% \FFrj \baselineskip = 20pt
%   \FFrl \baselineskip = 24pt



\centerline{
Paypal @ norprofit
} 
{
% \FFrf \baselineskip = 14pt
https://www.paypal.com/us/smarthelp/article/how-can-i-get-my-nonprofit-set-up-with-paypal-to-accept-donations-faq1068
} 

\par PayPal can help your nonprofit organization easily accept donations from supporters. Most nonprofits choose PayPal Payments Standard or PayPal Checkout (formerly known as Express Checkout) as their payment solution. These options let your donors complete their transactions on the PayPal website. Note that you must have a PayPal Business account – not a Personal account – to accept donations for your organization. You’ll need to confirm your nonprofit status to be eligible for the lower nonprofit transaction rate.
\par Be prepared to provide the following information:
\par Evidence of nonprofit registration with any applicable regulatory body, such as Articles of Incorporation, IRS 501(c)(3) determination letter or documentation of candidacy.
\par A pre-printed bank statement or voided check from your account. Starter checks are not acceptable. The organization needs to own each bank account linked to this PayPal account. You can't use a personal bank account.
\par Information about how you intend to use the money (such as donations or membership fees).
\par Your mission statement (if applicable).
\par A subordination or fundraising letter (if applicable).
\par We use these documents for several reasons:
\par To verify that your nonprofit is registered, because we offer discounted rates to 501(c)(3) organizations.
\par To ensure we’re meeting our regulatory requirements for the government.
\par To reassure donors that their money is going to a registered nonprofit organization.
\par Special rates for 501(c)(3)
\par We offer discounted fees for registered nonprofit organizations with 501(c)(3) status. If you transact between \$0 and \$100,000, you’ll pay a discounted flat-rate fee. For anything over \$100,000, please call: 1-855-787-1012.
\par To apply for the nonprofit rate, click here.
\par If you don’t have 501(c)(3) status, PayPal still offers a simple flat-rate fee.
\par Add a PayPal Donate Button to your Site Now
\par Learn more about all the tools PayPal provides to help nonprofits raise funds at PayPal Nonprofits.

\bye
