\input ../header/example_tex01.tex

\centerline{ \FFbg
Resume of Yanuo Deng (James)
}

\centerline{ % \FFbb
1565 Cress Way, Olivehurst,CA,95961
*
(408)444-5520
*
deng.ya.nuo@gmail.com
}

{ \medbreak } { \FFbg
CAREER OBJECTIVE
}

{ \smallbreak } {\par\noindent\hrule} { \smallbreak }

    Focused professional with 15+ years of experience
and a proven knowledge of embedded system(linux/RTOS),
and digital \& analogy circuit design.
    Aiming to leverage my skills to be a successfully
Integrated Circuit Engineer,
Software Engineer,
or Network Security Engineer.

{ \medbreak } { \FFbg
EXPERIENCE
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }

{ \medbreak } { \FFbg
C-MATRIXTECH CO.LTD., Zhuhai, China, 3 people R\&D/6
}

{ \FFte
Integrated Circuit Designer, Dec 2017 - Feb 2019
}

{ \parindent = 1 em \item{*}
 Verilog coding, FPGA simulation and debug for self-powered SOC chip.
}

{ \parindent = 1 em \item{*}
 MCU debug; Port C-language from Assembly for the MCU; Mixed (Analog) circuit design
}
{ \parindent = 1 em \item{*}
 Achieved self-powered MCU SOC used on iPhone data cables; Mass production 10k/M
}

{ \medbreak } { \FFbg
VIOMI CO.LTD., Foshan, China, 3 people R\&D/200
}

{ \FFte
Software (Firmware) Engineer, May 2017 - Oct 2017
}

{ \parindent = 1 em \item{*}
 Linux driver for the Wi-Fi chip; Speech Recognition App for Linux
 }
{ \parindent = 1 em \item{*}
 Achieved smart wireless Speech Recognition module ; Mass production 3k/M
 }

{ \medbreak } { \FFbg
BLUEWAY CO.LTD., Huizhou, China, 5 people R\&D/2500
}

{ \FFte
Software (Firmware) Engineer, May 2016 - Apr 2017
}
{ \parindent = 1 em \item{*}
 FreeRTOS system migration to STM32 for the embedded board, target for electric mowers
 }

{ \medbreak } { \FFbg
ADON CO.LTD., Foshan, China, 3 people R\&D/350
}

{ \FFte
Software (Firmware) Engineer, Oct 2013 - Dec 2015
}
{ \parindent = 1 em \item{*}
 Linux driver \& app for the Homepod (Wi-Fi speaker/charger for iPhone); Mass production, 3k/M
 }

{ \medbreak } { \FFbg
SKYIT SOFTWARE CO.LTD., Shunde, China, 5 people R\&D/500
}

{ \FFte
Software Engineer, Dec 2011 - Jul 2013
}
{ \parindent = 1 em \item{*}
 Windows Client App by C\#; Data API by C for the first order a meal Android App in China
 }

{ \medbreak } { \FFbg
VBRIDGE MICROSYSTEM INC, San Jose, CA, 5 people R\&D/12
}

{ \FFte
Digital Integrated Circuit Engineer, Apr 2005 - May 2008
}
{ \parindent = 1 em \item{*}
 IP cores of security engineer :
 AES, DES, 3DES, MD5, SHA1, CRC ;
 5-bits MCU core.
 }
{ \parindent = 1 em \item{*}
All IP cores tapout in a dual-MIPS SOC Chip.
 }
{ \parindent = 1 em \item{*}
Linux + VxWorks board support package(BSP) was built for the dual-MIPS.
 }

{ \medbreak } { \FFbg
EDUCATION
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
XI'AN university of technology, Xi'an city, Shannxi, China

{ \FFte
Master of Science (M.S.) Microelectronics \& Solid State Electronics (Apr 2005)
}

{ \medbreak } { \FFbg
ADDITIONAL SKILLS
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
{ \parindent = 1 em \item{*}
 C, Verilog, Vim, Bash, Perl, Go-language, Gnumake, git
 }
{ \parindent = 1 em \item{*}
 Linux / FreeRTOS driver
 }

{ \medbreak } { \FFbg
Certifications
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
Electronics Engineer Certification, Foshan , China , Aug 2008

{ \medbreak } { \FFbg
Personal Characteristics
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
%I am a experienced software engineer in digital \& analog circuit design, and embedded system design.
%Usually I take care of the base framework coding in the teamwork group. When discussing, I am aggressive and creative, trying to find the best solution together. When coding, I am stable and firm. I prefer to provide long term service to the company.
I work well within teams, and I am assertive and creative
    in finding the best solutions for the team.
I am known to be stable and firm when coding.
I am committed to achieving goals set for me.
I speak and write
Cantonese/Mandarin.

{ \medbreak } { \FFbg
Referrals
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }

Dan Teuthorn, 
Teledyne microwave solutions, VP engineer,
408-421-7303,
Den.Teuthorn@teledyne.com

Tang Shanqiang,
Cadence,
Principal Application Engineer,
+65-90546301,
ansent@cadence.com

Stephen Fung,
Atheros/Qualcomm , semicondutor engineer,
408-338-5175,
stephen@thepoint.church

% Arsenia Harrison,
% One More Chance Company, CEO,
% 916-271-3054,
% Arseniaharrison@aol.com

% Khinmien Chong, 
% STATS ChipPAC Ltd.,
% 408-819-8676,
% khinmienchong@gmail.com

{ \medbreak } 
{ % \FFbg
USA Employment Authorization Document(EAD) valided from 2021 to 2023.
No work sponsor is needed.
}

\break

\bye
