\special{papersize=8.5in,11.5in}
% % 0.4 padding 
% \hsize 7.7 in     % 8.5  - 0.4 * 2
% \vsize 10.7 in    % 11.5 - 0.4 * 2
% \voffset -0.6 in  % 1 - 0.4
% \hoffset -0.6 in  % 1 - 0.4

% 0.7 padding
\hsize 7.1 in     % 8.5  - 0.7 * 2
\vsize 10.1 in    % 11.5 - 0.7 * 2
\voffset -0.3 in  % 1 - 0.7
\hoffset -0.3 in  % 1 - 0.7

% \hsize 6.9 in     % 8.5  - 0.8 * 2
% \vsize 9.9 in     % 11.5 - 0.8 * 2
% \special{papersize=8.5in,11.5in}
% % 0.4 padding 
% \voffset -0.2 in  % 1 - 0.8
% \hoffset -0.2 in  % 1 - 0.8

\nopagenumbers

\parindent = 0 pt
\emergencystretch = 800 em
%\tolerance=10000
%\baselineskip = 16pt
\baselineskip = 12pt


\font\FFaa=      cmb10            at 24pt
%\font\FFbb=      cmr10            at 8.5pt
\font\FFbb=      cmr10            at 11pt
\font\FFcc=      cmb10            at 13pt
\font\FFdd=      cmb10            at 13pt
\font\FFee=      cmti10           at 13pt


\bigbreak

\centerline{ \FFaa
Resume of Yanuo Deng (James)
}

\centerline{ \FFbb
1565 Cress Way, Olivehurst,CA,95961
*
(408)444-5520
*
deng.ya.nuo@gmail.com
}

{ \medbreak } { \FFcc
CAREER OBJECTIVE
}

{ \smallbreak } {\par\noindent\hrule} { \smallbreak }

    Focused professional with 15+ years of experience 
and a proven knowledge of embedded system(linux/RTOS), 
and digital \& analogy circuit design. 
    Aming to leverage my skills to be a successfully 
Integrated Circuit Engineer, 
Software Engineer, 
or Network Security Engineer.

{ \medbreak } { \FFcc
EXPERIENCE
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }

{ \medbreak } { \FFdd
C-MATRIXTECH CO.LTD., Zhuhai, China, 3 person R\&D/6
}

{ \FFee
Integrated Circuit Designer, Dec 2017 - Feb 2019
}

{ \parindent = 1 em \item{*} 
 Verilog coding, FPGA simulation and debug for self-powered SOC chip. 
}

{ \parindent = 1 em \item{*} 
 MCU debug; Port C-language from Assembly for the MCU; Analog circuit design.
}
{ \parindent = 1 em \item{*} 
 Achieved self-powered MCU SOC used on iPhone data cables; Mass production 10 per month.
}

{ \medbreak } { \FFdd
VIOMI CO.LTD., Foshan, China, 3 person R\&D/200
}

{ \FFee
Software (Firmware) Engineer, May 2017 - Oct 2017
}

{ \parindent = 1 em \item{*} 
 Linux driver for the wifi chip; Speech Recognition App for Linux.
 }
{ \parindent = 1 em \item{*} 
 Achieved smart wireless Speech Recognition module ; Mass production 3k per month.
 }

{ \medbreak } { \FFdd
BLUEWAY CO.LTD., Huizhou, China, 5 person R\&D/2500
}

{ \FFee
Software (Firmware) Engineer, May 2016 - Apr 2017
}
{ \parindent = 1 em \item{*} 
 FreeRTOS system migration for the embedded board, target for electric mowers.
 }

{ \medbreak } { \FFdd
ADON CO.LTD., Foshan, China, 3 person R\&D/350
}

{ \FFee
Software (Firmware) Engineer, Oct 2013 - Dec 2015
}
{ \parindent = 1 em \item{*} 
 Linux driver \& app for the Homepod (wifi speaker/charger for iPhone); Mass production, 3k per month.
 }

{ \medbreak } { \FFdd
SKYIT SOFTWARE CO.LTD., Shunde, China, 5 person R\&D/500
}

{ \FFee
Software Engineer, Dec 2011 - Jul 2013
}
{ \parindent = 1 em \item{*} 
 Windows Client App by C\#; Data API by C for the first order a meal App in China
 }

{ \medbreak } { \FFdd
VBRIDGE MICROSYSTEM INC, San Jose, CA, 5 person R\&D/12
}

{ \FFee
Digital Integrated Circuit Engineer, Apr 2005 - May 2008
}
{ \parindent = 1 em \item{*} 
 AES, DES, 3DES, MD5, SHA1, CRC : IP cores for the security engineer. 
 }
{ \parindent = 1 em \item{*} 
 5 bit MCU for the dual-MIPS SOC chip
 }
{ \parindent = 1 em \item{*} 
 All IP cores include specification, testbench, RTL; All IP cores verified by the SOC Chip
 }

{ \medbreak } { \FFdd
EDUCATION
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
XI'AN university of technology, Xi'an city, Shannxi, China

{ \FFee
Master of Science (M.S.) Microelectronics \& Solidstate Electronics (Apr 2005)
}

{ \medbreak } { \FFdd
ADDITIONAL SKILLS
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
{ \parindent = 1 em \item{*} 
 C, Verilog, Vim, Bash, Perl, Go-language, Gnumake, git
 }
{ \parindent = 1 em \item{*} 
 Linux / FreeRTOS driver
 }

{ \medbreak } { \FFdd
Certifications
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
Electronics Engineer Certification, Foshan , China , Aug 2008

{ \medbreak } { \FFdd
Personal Characteristics
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }
%I am a experienced software engineer in digital \& analog circuit design, and embedded system design. 
%Usually I take care of the base framework coding in the teamwork group. When discussing, I am aggressive and creative, trying to find the best solution together. When coding, I am stable and firm. I prefer to provide long term service to the company.
I work well within teams and I am assertive and creative 
    in finding the best solutions for the team.
I am known to be stable and firm when coding.
I am committed to achieving goals set for me.
I speak and write 
Cantonese/Mandarin.

{ \medbreak } { \FFdd
Referrals
}
{ \smallbreak } {\par\noindent\hrule} { \smallbreak }

Stephen Fung,
Atheros/Qualcomm , semicondutor Engineer,
Church members,
408-338-5175,
stephen@thepoint.church

Arsenia Harrison,
One More Chance Company,
CEO,
counselor,
916-271-3054,
Arseniaharrison@aol.com

{ \medbreak } 
{ % \FFdd
USA Employment Authorization Document(EAD) valided from Feb 2021 to Feb 2023.
}

\break

\bye
