\documentclass{article}
\usepackage[utf8]{inputenc}

\title{
Yanuo Deng (James)x
}

\author{}
\date{ }

\begin{document}
\maketitle

1565 Cress Way, Olivehurst,CA,95961
(408)444-5520
deng.ya.nuo@gmail.com
Cantonese

CAREER OBJECTIVE
---
Focused professional with 15+ years of experience and a proven knowledge of embedded system(linux/RTOS), and digital \& analogy circuit design. Amiing to leverage my skills to successfully fill the Integrated Circuit Engineer, Software Engineer, or Network Security Engineer role at your company.

EXPERIENCE
---
C-MATRIXTECH CO.LTD., Zhuhai, Guangdong, 3 person R\&D/6
Integrated Circuit Designer, Dec 2017 - Feb 2019
 Verilog coding, FPGA simulation and debug for self-powered SOC chip. 
 MCU debug; Port C-language from Assembly for the MCU; Analog circuit design.
 Achieved self-powered MCU SOC used on iPhone data cables; Mass production 10 per month.

VIOMI CO.LTD., Foshan, Guangdong, 3 person R\&D/200
Software (Firmware) Engineer, May 2017 - Oct 2017
 Linux driver for the wifi chip; Speech Recognition App for Linux.
 Achieved smart wireless Speech Recognition module ; Mass production 3k per month.

BLUEWAY CO.LTD., Huizhou, Guangdong, 5 person R\&D/2500
Software (Firmware) Engineer, May 2016 - Apr 2017
 FreeRTOS system migration for the embedded board, target for electric mowers.

ADON CO.LTD., Foshan, Guangdong, 3 person R\&D/350
Software (Firmware) Engineer, Oct 2013 - Dec 2015
 Linux driver \& app for the Homepod (wifi speaker/charger for iPhone); Mass production, 3k per month.

SKYIT SOFTWARE CO.LTD., Shunde, Guangdong, 5 person R\&D/500
Software Engineer, Dec 2011 - Jul 2013
 Windows Client App by C\#; Data API by C for the first order a meal App in China

VBRIDGE MICROSYSTEM INC, San Jose, CA, 5 person R\&D/12
Digital Integrated Circuit Engineer, Apr 2005 - May 2008
 AES, DES, 3DES, MD5, SHA1, CRC : ipcores for the security engineer. 
 5 bit MCU for the dual-MIPS SOC chip
 All IP cores include specification, testbench, RTL; All IP cores verified by the SOC Chip

EDUCATION
---
XI'AN university of technology, Xi'an city, Shannxi, China
Master of Science (M.S.) Microelectronics \& Solidstate Electronics (Apr 2005)

ADDITIONAL SKILLS
---
 C, Verilog, Vim, Bash, Perl, Go-language, Gnumake, git
 Linux / FreeRTOS driver

Certifications
---
Electronics Engineer Certification, Foshan city, Aug 2008

\end{document}
